---
title: "Assignment 1"
author: "Shixuan Weng"
date: "2023-11-13"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Assignment 1

This assignment1 included a function to calculate the mean value of a random numeric vector of length 50 and generating a scatter plot using the plot() function.

### Load your own .csv file into R, report the dimension of your data frame, then generate a scatter plot using the plot() function.

```{r myscatplot, echo=TRUE}
#绘制某港口货物吞吐量和年份的关系
library("ggplot2")
throughput <- read.csv("throughput.csv")
throughput |> dim()
plot(x=throughput$year, y=throughput$throughput,
     pch=20, col=adjustcolor("darkblue", 1/2),
     xlab="Year", ylab="Cargo throughput (billion tons)")
```

### Write a loop to calculate the mean value of a random numeric vector of length 50

```{r mean2random}
mean2 <- function(x){
  sum <- 0
  for (i in 1:length(x)){
    sum <- sum + x[i]
  }
  sum/length(x)
}

vec1 <- rnorm(50)
mean2(vec1)
```